\heiti \Large 我的五子棋AI果然有问题

### 2020-12-10 paper/paper.tex
final

    \begin{python}
        print (hello world)
    \end{python}
    \section{测试}

    \section{结束语}
    \subsection{研究总结}
    1.	本组对棋类博弈人工智能的发展历程进行了了解，学习了博弈树、局面评估函数、卡罗蒙特树等相关算法，对当代的五子棋AI进行研究分析，从而确定了本组的研究目标与研究方向。\par
2.	本组开展了对自我学习算法的探索与实践，将蒙特卡洛树搜索与自我对局相结合，提高了训练数据的有效度。同时对博弈树进行了一定的剪枝，降低了博弈树搜索的时间复杂度，减少了不必要学习的局面。\par
3.	本组利用卷积神经网络进行模型的构筑，并且在此之上基于策略价值网络的设计，在一定程度上消除了传统方法带来的缺陷与不足。同时利用数据的扩充和反向传播算法的改进，实现了AI的自我学习能力。\par
    \subsection{工作展望}
    1.	由于本组未使用拥有足够强算力的计算机以及时间问题，本组的人工智能并未达到一个很高的层次，我们的人工智能还存在巨大的提升空间，本组可能在将来继续进行对该人工智能的训练。\par
    2.	本文对于剪枝算法和蒙特卡洛树的研究并不透彻，其中存在大量未被使用的剪枝算法可以用于提升人工智能的AI，故在这一方面还需进行更进一步的研究。\par
    \newpage
    \addcontentsline{toc}{section}{参考文献}
    \begin{thebibliography}{30}%参考文献
    \bibitem{ref1}{李金洪\ 深度学习之TensorFlow\ [M]\ .北京.机械工业出版社, 2018-3}
    \bibitem{b1}{ 陈东焰,陆畅.从AlphaGo看机器学习[J].科技创新导报,2020,17(13):146-148. }
    \bibitem{b3}{百度百科 AlphaGo }
    \bibitem{b2}{计算机围棋AlphaGo算法对人类围棋算法的影响[J]. 程思雨,林锋.  中国科技信息. 2019(02)}
    \bibitem{ref2}{naka. J., The weakest Othello, Takujin Yoshida.Thoroughly dig into the inside of the development!(2019-7-25) [2020-09-01]https://ai-trend.jp/business-article/interview/othello-cto-interview}
    \bibitem{ref3}{菜鸟教程 python基础教程 https://www.runoob.com/
    python/python-tutorial.html}
    \bibitem{ref4}{董慧颖;王杨．多种搜索算法的五子棋博弈算法研究[J]．沈阳理工大学学报，2017,2}
    \bibitem{k1}{沈大旺.基于人工智能的五子棋搜索算法[J].产业与科技论坛,2020,19(01):73-74.
http://nooverfit.com/wp/%E8%92%99%E7%89%B9%E5%8D%A1%E6%B4%9B%E6%A0%91%E6%90%9C%E7%B4%A2-mcts-%E5%85%A5%E9%97%A8/
}
    \bibitem{k2}{知乎;匿名用户 蒙特卡洛树是什么算法？2017-05-09 https://www.zhihu.com/question/39916945}
    \bibitem{k3}{刘建平Pinard的博客 强化学习(十八) 基于模拟的搜索与蒙特卡罗树搜索(MCTS) 2019-03-04 https://www.cnblogs.com/pinard/p/10470571.html}
    \bibitem{k4}{yif25博客 蒙特卡罗树搜索（MCTS）2018-01-17 16:07 https://www.cnblogs.com/yifdu25/p/8303462.html}
    \bibitem{k5}{知乎; Xiaohu Zhu 蒙特卡洛树搜索简介 https://zhuanlan.zhihu.com/p/30316076}
    \bibitem{k6}{基于蒙特卡洛树搜索的计算机围棋博弈研究[D]. 于永波.大连海事大学 2015}
    \bibitem{k7}{林华. 基于Self-Play的五子棋智能博弈机器人[D].浙江大学,2019.}
    \bibitem{k8}{知乎 叉色-xsir 五子棋的谱库设计与实现 https://zhuanlan.zhihu.com/p/88598278}
    \bibitem{k9}{李昊. 五子棋人机博弈算法优化研究与实现[D].大连海事大学,2020.}
    \bibitem{k10}{David Silver, Aja Huang.Mastering the game of Go with deep neural networks and tree search[J].Nature, 2016, 14(3)}
    \bibitem{AI1}{扶潇. 基于机器学习的围棋策略网络模型的数据优化[D].北京邮电大学,2017.}
    \bibitem{AI2}{CSDN BBlue-Sky AlphaGo Zero详解 https://
    blog.csdn.net/qq\_33813365/article/\par
    details/103344018}
\bibitem{L1}{沈大旺.基于人工智能的五子棋搜索算法[J].产业与科技论坛,2020,19(01):73-74.}
\bibitem{L2}赵美勇,宋思睿.博弈论算法在AI中的应用[J].计算机产品与流通,2019(09):278.
\bibitem{L3}郑健磊,匡芳君.基于极小极大值搜索和Alpha Beta剪枝算法的五子棋智能博弈算法研究与实现[J].温州大学学报(自然科学版),2019,40(03):53-62.
\bibitem{L4}牛恺泽,邓鑫.五子棋人工智能研究与实践[J].数字通信世界,2019(01):32-33.
\bibitem{L5}孙世文.五子棋人工智能算法实现研究[J].中国新通信,2018,20(23):143.
\bibitem{L6}张效见. 五子棋计算机博弈系统的研究与设计[D].安徽大学,2017.
\bibitem{L7}董慧颖,王杨.多种搜索算法的五子棋博弈算法研究[J].沈阳理工大学学报,2017,36(02):39-43+83.
\bibitem{L8}邢森.五子棋智能博弈的研究与设计[J].电脑知识与技术,2010,6(13):3497-3498.
\bibitem{L9}张明亮,李凡长.一种新的博弈树搜索方法[J].山东大学学报(工学版),2009,39(06):1-7+23.
    \end{thebibliography}
    \newpage
\end{multicols}
\end{document}

>>>>

  这里可以通过修改Ai\_or\_notAI ='AI'来选择是否和人工智能对战
  \begin{lstlisting}[language=Python,breaklines = true]
####################
# author:happys
# coding:UTF8
# 程序目的：程序进入的入口
###################
# from AI.train import *
# training_pipeline = TrainPipeline()
# training_pipeline.run()
#
from AI.human_play import *
Ai_or_notAI = 'AI'  # 选择智能还是智障
# Ai_or_notAI = 'notAI'#选择智能还是智障
run(Ai_or_notAI)
  \end{lstlisting}
  \subsection{UI界面}
  UI\_Board.py
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
# code:utf-8
# author:zkl,白炎
from time import sleep
import pygame
import tkinter
import tkinter.messagebox
from pygame.locals import *
from enum import Enum
# 颜色RGB
from UI import BoardData
class Color(Enum):
  WHITE = 0
  BLACK = 1
  RED = (255, 0, 0)
# 棋子类
class chess():
  # 初始化
  def __init__(self, screen, color, row, column):
    self.screen = screen
    self.image = pygame.image.load("AI/Images/chess" + str(color.value) + ".png")
    self.image = pygame.transform.scale(self.image, (Chessboard.UNIT * 2, Chessboard.UNIT * 2))
    self.pos = Chessboard.convertArrayToPos(row, column)
    self.rect = self.image.get_rect()
    self.rect = self.pos
    self.screen.blit(self.image, self.rect)
# 棋盘类
class Chessboard:

  # 初始化棋盘
  def __init__(self, board_data, UNIT=35, width=50):
    self.ROW = board_data.row
    self.COLUMN = board_data.column
    Chessboard.UNIT = UNIT
    Chessboard.width = width

  # 绘制棋盘, 传入当前棋盘，窗口，边框宽度
  def drawmap(self, screen, width):
    # 行
  for row in range(self.COLUMN):
    pygame.draw.line(screen, Color.RED.value,(width, width + row * self.UNIT),(width + self.UNIT * (self.ROW - 1),width + row * self.UNIT))
    # 列
  for column in range(self.ROW):
    pygame.draw.line(screen, Color.RED.value,(width + column * self.UNIT, width),(width + column * self.UNIT,width + self.UNIT * (self.COLUMN - 1)))
  @staticmethod
  def convertArrayToPos(row, column):
    return Chessboard.width + (row - 1) * Chessboard.UNIT, Chessboard.width + (column - 1) * Chessboard.UNIT

  @staticmethod
  def convertPosToArray(x, y):
    return (x - Chessboard.width // 2) // Chessboard.UNIT, (y - Chessboard.width // 2) // Chessboard.UNIT

class bboard:
  def __init__(self,boardData):
    self.boardData=boardData

# 主程序
# 初始化界面

screen = 1

def set_human(human):
  global Human
  Human=human

def init_game():
  # 设置边框宽度
  BOARD_WIDTH = 50
  # 创建棋盘
  global boardData
  boardData = BoardData.BoardData(8, 8)
  chessBoard = Chessboard(boardData)
  pygame.init()

  SIZE = (2 * BOARD_WIDTH + chessBoard.UNIT * (chessBoard.ROW - 1),
    2 * BOARD_WIDTH + chessBoard.UNIT * (chessBoard.COLUMN - 1))
  # 创建窗口
  global screen
  screen = pygame.display.set_mode(SIZE)
  # 设置窗口标题
  pygame.display.set_caption("我的五子棋AI果然有问题")
  # 设置背景
  background = pygame.image.load('AI/Images/bg.jpg')
  background = pygame.transform.scale(background, SIZE)

  screen.blit(background, (0, 0))
  # #绘制棋盘
  # Chessboard.drawmap(screen,BOARD_WIDTH)
  chessBoard.drawmap(screen, 50)

  pygame.display.update()

def updateBoard(board):
  if boardData:
    boardData.transportToBoardData(board)
    showChess()

# To solve mouse click event
def checkEvent(event):
  if event.type == MOUSEBUTTONDOWN:
    row, column = Chessboard.convertPosToArray(event.pos[0], event.pos[1])
    putChessOnBoard(row, column)
    pygame.display.update()
  pass

def putChessOnBoard(row, column):
  # pass
  print(row,column)
  if Human!=None:
    Human.give_input(boardData.row-1-column,row)
  # Human.give_input(row,column)
  # isWin = boardData.putChess(row, column)
  # if isWin != False:
  #   chessNew = chess(screen, Color.WHITE if boardData.thisTurn else Color.BLACK, row, column)
  #   print(row,column)
  # print(isWin)
  # if isWin:
  #   tkinter.messagebox.askokcancel(title="Who Won?", message="White won" if boardData.thisTurn else "Black won");
  #   init_game()
  # return isWin

def showChess():
  for i in range(boardData.row):
    for j in range(boardData.column):
    if boardData.getBoard()[i][j]==1:
      chessNew=chess(screen, Color.WHITE , i, j)
    elif boardData.getBoard()[i][j]==-1:
      chessNew = chess(screen, Color.BLACK, i, j)
  pygame.display.update()

# 控制游戏进程
def open_UI():

  # init_game()
  while True:
    sleep(0.5)
    for event in pygame.event.get():
    if event.type == QUIT:
      exit()
    else:
      checkEvent(event)

if __name__=="__main__":
  open_UI()
  \end{lstlisting}\par
  BoardData.py
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
    # author:白炎拉力

import numpy as np
from enum import Enum

class Chess(Enum):
  White = 1
  Black = -1

class BoardData:
  # in array board, 1 means white chess, -1 means black chess, 0 means nothing
  thisTurn = False  # this turn is true when it's white chess ready to put

  def __init__(self, row, column):
    self.row = row
    self.column = column
    print([row, column])
    self.board = np.zeros((row, column), dtype=int)

  def getBoard(self):
    # print(self.board)
    return self.board

  def transportToBoardData(self, boardFromGame):
    for location in boardFromGame.states:
    x=self.row - 1 - location // self.row
    y=location % self.row
    # temp=x
    # x=(self.row-1)-y
    # y=(self.row-1)-temp
    temp=x
    x=y
    y=temp
    if boardFromGame.states[location] == 1:
      self.board[x][y] = 1
    elif boardFromGame.states[location] == 2:
      self.board[x][y] = -1
    else:
      self.board[x][y] = 0

  def putChess(self, row, column):
    if row >= self.row or column >= self.column or row < 0 or column < 0:
    return False
    if self.board[row, column] == 0:
    if self.thisTurn:
      self.board[row, column] = 1
    else:
      self.board[row, column] = -1
    if self.checkWin(row, column):
      return True
    self.thisTurn = not self.thisTurn
    else:
    return False

  def checkWinAll(self):
    for row in range(len(self.board)):
    for column in range(len(self.board[0])):
      if self.checkWin(row, column):
        return True
    return False

  def checkWin(self, row, column):
    color = self.board[row, column]
    directions = ((1, 0), (0, 1), (1, 1), (1, -1))
    if (color == 0): return False
    for direction in directions:
    count = 1
    step = 1
    while self.inBound(row + direction[0] * step, column + direction[1] * step) and color == self.board[
      row + direction[0] * step, column + direction[1] * step]:
      count += 1
      step += 1
      if count == 5: return True
    step = 1
    while self.inBound(row - direction[0] * step, column - direction[1] * step) and color == self.board[
      row - direction[0] * step, column - direction[1] * step]:
      count += 1
      step += 1
      if count == 5: return True

  def inBound(self, row, column):
    if 0 <= row < len(self.board) and 0 <= column < len(self.board[0]):
    return True
    else:
    return False

if __name__ == '__main__':
  board = BoardData(5, 5)
  for i in range(5):
    board.putChess(0, i)
    print(board.checkWinAll())
    board.putChess(1, i)
    board.getBoard()
  \end{lstlisting}
  \subsection{AI}
  policy\_value\_net\_pytorch.py训练模型
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
  # -*- coding: utf-8 -*-
"""
An implementation of the policyValueNet in PyTorch
Tested in PyTorch 0.2.0 and 0.3.0

"""

import torch
import torch.nn as nn
import torch.optim as optim
import torch.nn.functional as F
from torch.autograd import Variable
import numpy as np

def set_learning_rate(optimizer, lr):
  """Sets the learning rate to the given value"""
  for param_group in optimizer.param_groups:
    param_group['lr'] = lr

class Net(nn.Module):
  """policy-value network module"""
  def __init__(self, board_width, board_height):
    super(Net, self).__init__()

    self.board_width = board_width
    self.board_height = board_height
    # common layers
    self.conv1 = nn.Conv2d(4, 32, kernel_size=3, padding=1)
    self.conv2 = nn.Conv2d(32, 64, kernel_size=3, padding=1)
    self.conv3 = nn.Conv2d(64, 128, kernel_size=3, padding=1)
    # action policy layers
    self.act_conv1 = nn.Conv2d(128, 4, kernel_size=1)
    self.act_fc1 = nn.Linear(4*board_width*board_height,
           board_width*board_height)
    # state value layers
    self.val_conv1 = nn.Conv2d(128, 2, kernel_size=1)
    self.val_fc1 = nn.Linear(2*board_width*board_height, 64)
    self.val_fc2 = nn.Linear(64, 1)

  def forward(self, state_input):
    # common layers
    x = F.relu(self.conv1(state_input))
    x = F.relu(self.conv2(x))
    x = F.relu(self.conv3(x))
    # action policy layers
    x_act = F.relu(self.act_conv1(x))
    x_act = x_act.view(-1, 4*self.board_width*self.board_height)
    x_act = F.log_softmax(self.act_fc1(x_act))
    # state value layers
    x_val = F.relu(self.val_conv1(x))
    x_val = x_val.view(-1, 2*self.board_width*self.board_height)
    x_val = F.relu(self.val_fc1(x_val))
    x_val = F.tanh(self.val_fc2(x_val))
    return x_act, x_val

class PolicyValueNet():
  """policy-value network """
  def __init__(self, board_width, board_height,
       model_file=None, use_gpu=False):
    self.use_gpu = use_gpu
    self.board_width = board_width
    self.board_height = board_height
    self.l2_const = 1e-4  # coef of l2 penalty
    # the policy value net module
    if self.use_gpu:
    self.policy_value_net = Net(board_width, board_height).cuda()
    else:
    self.policy_value_net = Net(board_width, board_height)
    self.optimizer = optim.Adam(self.policy_value_net.parameters(),
            weight_decay=self.l2_const)

    if model_file:
    net_params = torch.load(model_file)
    self.policy_value_net.load_state_dict(net_params)

  def policy_value(self, state_batch):
    """
    input: a batch of states
    output: a batch of action probabilities and state values
    """
    if self.use_gpu:
    state_batch = Variable(torch.FloatTensor(state_batch).cuda())
    log_act_probs, value = self.policy_value_net(state_batch)
    act_probs = np.exp(log_act_probs.data.cpu().numpy())
    return act_probs, value.data.cpu().numpy()
    else:
    state_batch = Variable(torch.FloatTensor(state_batch))
    log_act_probs, value = self.policy_value_net(state_batch)
    act_probs = np.exp(log_act_probs.data.numpy())
    return act_probs, value.data.numpy()

  def policy_value_fn(self, board):
    """
    input: board
    output: a list of (action, probability) tuples for each available
    action and the score of the board state
    """
    legal_positions = board.availables
    current_state = np.ascontiguousarray(board.current_state().reshape(
      -1, 4, self.board_width, self.board_height))
    if self.use_gpu:
    log_act_probs, value = self.policy_value_net(
        Variable(torch.from_numpy(current_state)).cuda().float())
    act_probs = np.exp(log_act_probs.data.cpu().numpy().flatten())
    else:
    log_act_probs, value = self.policy_value_net(
        Variable(torch.from_numpy(current_state)).float())
    act_probs = np.exp(log_act_probs.data.numpy().flatten())
    act_probs = zip(legal_positions, act_probs[legal_positions])
    value = value.data[0][0]
    return act_probs, value

  def train_step(self, state_batch, mcts_probs, winner_batch, lr):
    """perform a training step"""
    # wrap in Variable
    if self.use_gpu:
    state_batch = Variable(torch.FloatTensor(state_batch).cuda())
    mcts_probs = Variable(torch.FloatTensor(mcts_probs).cuda())
    winner_batch = Variable(torch.FloatTensor(winner_batch).cuda())
    else:
    state_batch = Variable(torch.FloatTensor(state_batch))
    mcts_probs = Variable(torch.FloatTensor(mcts_probs))
    winner_batch = Variable(torch.FloatTensor(winner_batch))

    # zero the parameter gradients
    self.optimizer.zero_grad()
    # set learning rate
    set_learning_rate(self.optimizer, lr)

    # forward
    log_act_probs, value = self.policy_value_net(state_batch)
    # define the loss = (z - v)^2 - pi^T * log(p) + c||theta||^2
    # Note: the L2 penalty is incorporated in optimizer
    value_loss = F.mse_loss(value.view(-1), winner_batch)
    policy_loss = -torch.mean(torch.sum(mcts_probs*log_act_probs, 1))
    loss = value_loss + policy_loss
    # backward and optimize
    loss.backward()
    self.optimizer.step()
    # calc policy entropy, for monitoring only
    entropy = -torch.mean(
      torch.sum(torch.exp(log_act_probs) * log_act_probs, 1)
      )
    # return loss.data[0], entropy.data[0]
    #for pytorch version >= 0.5 please use the following line instead.
    return loss.item(), entropy.item()

  def get_policy_param(self):
    net_params = self.policy_value_net.state_dict()
    return net_params

  def save_model(self, model_file):
    """ save model params to file """
    net_params = self.get_policy_param()  # get model params
    torch.save(net_params, model_file)
  \end{lstlisting}
  游戏进程
  game.py
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
from __future__ import print_function
import numpy as np
from tkinter import messagebox
import UI.UI_Board
import sys
import threading

class Board(object):
  """board for the game"""

  def __init__(self, **kwargs):
    self.width = int(kwargs.get('width', 8))
    self.height = int(kwargs.get('height', 8))
    # board states stored as a dict,
    # key: move as location on the board,
    # value: player as pieces type
    self.states = {}
    # need how many pieces in a row to win
    self.n_in_row = int(kwargs.get('n_in_row', 5))
    self.players = [1, 2]  # player1 and player2

  def init_board(self, start_player=0):
    if self.width < self.n_in_row or self.height < self.n_in_row:
    raise Exception('board width and height can not be '
          'less than {}'.format(self.n_in_row))
    self.current_player = self.players[start_player]  # start player
    # keep available moves in a list
    self.availables = list(range(self.width * self.height))
    self.states = {}
    self.last_move = -1

  def move_to_location(self, move):
    """
    3*3 board's moves like:
    6 7 8
    3 4 5
    0 1 2
    and move 5's location is (1,2)
    """
    h = move // self.width
    w = move % self.width
    return [h, w]

  def location_to_move(self, location):
    if len(location) != 2:
    return -1
    h = location[0]
    w = location[1]
    move = h * self.width + w
    if move not in range(self.width * self.height):
    return -1
    return move

  def current_state(self):
    """return the board state from the perspective of the current player.
    state shape: 4*width*height
    """

    square_state = np.zeros((4, self.width, self.height))
    if self.states:
    moves, players = np.array(list(zip(*self.states.items())))
    move_curr = moves[players == self.current_player]
    move_oppo = moves[players != self.current_player]
    square_state[0][move_curr // self.width,
          move_curr % self.height] = 1.0
    square_state[1][move_oppo // self.width,
          move_oppo % self.height] = 1.0
    # indicate the last move location
    square_state[2][self.last_move // self.width,
          self.last_move % self.height] = 1.0
    if len(self.states) % 2 == 0:
    square_state[3][:, :] = 1.0  # indicate the colour to play
    return square_state[:, ::-1, :]

  def do_move(self, move):
    if(move==None):return
    self.states[move] = self.current_player
    self.availables.remove(move)
    self.current_player = (
    self.players[0] if self.current_player == self.players[1]
    else self.players[1]
    )
    self.last_move = move

  def has_a_winner(self):
    width = self.width
    height = self.height
    states = self.states
    n = self.n_in_row

    moved = list(set(range(width * height)) - set(self.availables))
    if len(moved) < self.n_in_row *2-1:
    return False, -1

    for m in moved:
    h = m // width
    w = m % width
    player = states[m]

    if (w in range(width - n + 1) and
        len(set(states.get(i, -1) for i in range(m, m + n))) == 1):
      return True, player

    if (h in range(height - n + 1) and
        len(set(states.get(i, -1) for i in range(m, m + n * width, width))) == 1):
      return True, player

    if (w in range(width - n + 1) and h in range(height - n + 1) and
        len(set(states.get(i, -1) for i in range(m, m + n * (width + 1), width + 1))) == 1):
      return True, player

    if (w in range(n - 1, width) and h in range(height - n + 1) and
        len(set(states.get(i, -1) for i in range(m, m + n * (width - 1), width - 1))) == 1):
      return True, player

    return False, -1

  def game_end(self):
    """Check whether the game is ended or not"""
    win, winner = self.has_a_winner()
    if win:
    return True, winner
    elif not len(self.availables):
    return True, -1
    return False, -1

  def get_current_player(self):
    return self.current_player

class Game(object):
  """game server"""

  def __init__(self, board, **kwargs):
    self.board = board  # type: Board

  def showUI(self,board):
    UI.UI_Board.updateBoard(board)
    # globalVar.get_value("boardData").transportToBoardData(board)
    # UI.UI_Board.boardData.transportToBoardData(board)
    # UI.UI_Board.showChess()
    pass

  def graphic(self, board, player1, player2):
    """Draw the board and show game info"""

    self.showUI(board)

    width = board.width
    height = board.height

    print("Player", player1, "with X".rjust(3))
    print("Player", player2, "with O".rjust(3))
    print()
    for x in range(width):
    print("{0:8}".format(x), end='')
    print('\r\n')
    for i in range(height - 1, -1, -1):
    print("{0:4d}".format(i), end='')
    for j in range(width):
      loc = i * width + j
      p = board.states.get(loc, -1)
      if p == player1:
        print('X'.center(8), end='')
      elif p == player2:
        print('O'.center(8), end='')
      else:
        print('_'.center(8), end='')
    print('\r\n\r\n')

  def start_play(self, player1, player2, start_player=0, is_shown=1):
    """start a game between two players"""
    if start_player not in (0, 1):
    raise Exception('start_player should be either 0 (player1 first) '
          'or 1 (player2 first)')
    self.board.init_board(start_player)
    UI.UI_Board.set_human(None)
    UI.UI_Board.init_game()
    t2=threading.Thread(target=self.start_play1,args=(player1, player2, start_player, is_shown) )
    t2.start()
    target=threading.Thread(target=UI.UI_Board.open_UI())
    target.start()

  def start_play1(self,player1, player2, start_player=0, is_shown=1):
    p1, p2 = self.board.players
    player1.set_player_ind(p1)
    player2.set_player_ind(p2)
    players = {p1: player1, p2: player2}
    if is_shown:
    self.graphic(self.board, player1.player, player2.player)
    while True:
    current_player = self.board.get_current_player()
    player_in_turn = players[current_player]
    if(type(player_in_turn).__name__=="Human"):
      UI.UI_Board.set_human(player_in_turn)
    #TODO: Change the action
    move = player_in_turn.get_action(self.board)
    if move==None:
      continue
    self.board.do_move(move)
    if is_shown:
      self.graphic(self.board, player1.player, player2.player)
    end, winner = self.board.game_end()
    if end:
      if is_shown:
        if winner != -1:
        print("Game end. Winner is", players[winner])
        if(winner == 1):
          messagebox.showinfo('You win', '恭喜您获胜')
        else:
          messagebox.showinfo('You lose','您输了')
        else:
        print("Game end. Tie")
      return winner

  def start_self_play(self, player, is_shown=0, temp=1e-3):
    """ start a self-play game using a MCTS player, reuse the search tree,
    and store the self-play data: (state, mcts_probs, z) for training
    """
    self.board.init_board()
    p1, p2 = self.board.players
    states, mcts_probs, current_players = [], [], []
    while True:
    move, move_probs = player.get_action(self.board,
                 temp=temp,
                 return_prob=1)
    # store the data
    states.append(self.board.current_state())
    mcts_probs.append(move_probs)
    current_players.append(self.board.current_player)
    # perform a move
    self.board.do_move(move)
    if is_shown:
      self.graphic(self.board, p1, p2)
    end, winner = self.board.game_end()
    if end:
      # winner from the perspective of the current player of each state
      winners_z = np.zeros(len(current_players))
      if winner != -1:
        winners_z[np.array(current_players) == winner] = 1.0
        winners_z[np.array(current_players) != winner] = -1.0
      # reset MCTS root node
      player.reset_player()
      if is_shown:
        if winner != -1:
        print("Game end. Winner is player:", winner)
        else:
        print("Game end. Tie")
      return winner, zip(states, mcts_probs, winners_z)
  \end{lstlisting}
  价值网络矩阵policy\_value\_net\_numpy.py
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
  # -*- coding: utf-8 -*-
"""
Implement the policy value network using numpy, so that we can play with the
trained AI model without installing any DL framwork

"""

from __future__ import print_function
import numpy as np

# some utility functions
def softmax(x):
  probs = np.exp(x - np.max(x))
  probs /= np.sum(probs)
  return probs

def relu(X):
  out = np.maximum(X, 0)
  return out

def conv_forward(X, W, b, stride=1, padding=1):
  n_filters, d_filter, h_filter, w_filter = W.shape
  # theano conv2d flips the filters (rotate 180 degree) first
  # while doing the calculation
  W = W[:, :, ::-1, ::-1]
  n_x, d_x, h_x, w_x = X.shape
  h_out = (h_x - h_filter + 2 * padding) / stride + 1
  w_out = (w_x - w_filter + 2 * padding) / stride + 1
  h_out, w_out = int(h_out), int(w_out)
  X_col = im2col_indices(X, h_filter, w_filter,
         padding=padding, stride=stride)
  W_col = W.reshape(n_filters, -1)
  out = (np.dot(W_col, X_col).T + b).T
  out = out.reshape(n_filters, h_out, w_out, n_x)
  out = out.transpose(3, 0, 1, 2)
  return out

def fc_forward(X, W, b):
  out = np.dot(X, W) + b
  return out

def get_im2col_indices(x_shape, field_height,
         field_width, padding=1, stride=1):
  # First figure out what the size of the output should be
  N, C, H, W = x_shape
  assert (H + 2 * padding - field_height) % stride == 0
  assert (W + 2 * padding - field_height) % stride == 0
  out_height = int((H + 2 * padding - field_height) / stride + 1)
  out_width = int((W + 2 * padding - field_width) / stride + 1)

  i0 = np.repeat(np.arange(field_height), field_width)
  i0 = np.tile(i0, C)
  i1 = stride * np.repeat(np.arange(out_height), out_width)
  j0 = np.tile(np.arange(field_width), field_height * C)
  j1 = stride * np.tile(np.arange(out_width), out_height)
  i = i0.reshape(-1, 1) + i1.reshape(1, -1)
  j = j0.reshape(-1, 1) + j1.reshape(1, -1)

  k = np.repeat(np.arange(C), field_height * field_width).reshape(-1, 1)

  return (k.astype(int), i.astype(int), j.astype(int))

def im2col_indices(x, field_height, field_width, padding=1, stride=1):
  """ An implementation of im2col based on some fancy indexing """
  # Zero-pad the input
  p = padding
  x_padded = np.pad(x, ((0, 0), (0, 0), (p, p), (p, p)), mode='constant')

  k, i, j = get_im2col_indices(x.shape, field_height,
           field_width, padding, stride)

  cols = x_padded[:, k, i, j]
  C = x.shape[1]
  cols = cols.transpose(1, 2, 0).reshape(field_height * field_width * C, -1)
  return cols

class PolicyValueNetNumpy():
  """policy-value network in numpy """
  def __init__(self, board_width, board_height, net_params):
    self.board_width = board_width
    self.board_height = board_height
    self.params = net_params

  def policy_value_fn(self, board):
    """
    input: board
    output: a list of (action, probability) tuples for each available
    action and the score of the board state
    """
    legal_positions = board.availables
    current_state = board.current_state()

    X = current_state.reshape(-1, 4, self.board_width, self.board_height)
    # first 3 conv layers with ReLu nonlinearity
    for i in [0, 2, 4]:
    X = relu(conv_forward(X, self.params[i], self.params[i+1]))
    # policy head
    X_p = relu(conv_forward(X, self.params[6], self.params[7], padding=0))
    X_p = fc_forward(X_p.flatten(), self.params[8], self.params[9])
    act_probs = softmax(X_p)
    # value head
    X_v = relu(conv_forward(X, self.params[10],
            self.params[11], padding=0))
    X_v = relu(fc_forward(X_v.flatten(), self.params[12], self.params[13]))
    value = np.tanh(fc_forward(X_v, self.params[14], self.params[15]))[0]
    act_probs = zip(legal_positions, act_probs.flatten()[legal_positions])
    return act_probs, value
  \end{lstlisting}
  MCTS模型实现
  \begin{lstlisting}[language=Python,breaklines = true,columns=flexible]
  # -*- coding: utf-8 -*-
"""
A pure implementation of the Monte Carlo Tree Search (MCTS)

"""

import numpy as np
import copy
from operator import itemgetter

def rollout_policy_fn(board):
  """a coarse, fast version of policy_fn used in the rollout phase."""
  # rollout randomly
  action_probs = np.random.rand(len(board.availables))
  return zip(board.availables, action_probs)

def policy_value_fn(board):
  """a function that takes in a state and outputs a list of (action, probability)
  tuples and a score for the state"""
  # return uniform probabilities and 0 score for pure MCTS
  action_probs = np.ones(len(board.availables))/len(board.availables)
  return zip(board.availables, action_probs), 0

class TreeNode(object):
  """A node in the MCTS tree. Each node keeps track of its own value Q,
  prior probability P, and its visit-count-adjusted prior score u.
  """

  def __init__(self, parent, prior_p):
    self._parent = parent
    self._children = {}  # a map from action to TreeNode
    self._n_visits = 0
    self._Q = 0
    self._u = 0
    self._P = prior_p

  def expand(self, action_priors):
    """Expand tree by creating new children.
    action_priors: a list of tuples of actions and their prior probability
    according to the policy function.
    """
    for action, prob in action_priors:
    if action not in self._children:
      self._children[action] = TreeNode(self, prob)

  def select(self, c_puct):
    """Select action among children that gives maximum action value Q
    plus bonus u(P).
    Return: A tuple of (action, next_node)
    """
    return max(self._children.items(),
       key=lambda act_node: act_node[1].get_value(c_puct))

  def update(self, leaf_value):
    """Update node values from leaf evaluation.
    leaf_value: the value of subtree evaluation from the current player's
    perspective.
    """
    # Count visit.
    self._n_visits += 1
    # Update Q, a running average of values for all visits.
    self._Q += 1.0*(leaf_value - self._Q) / self._n_visits

  def update_recursive(self, leaf_value):
    """Like a call to update(), but applied recursively for all ancestors.
    """
    # If it is not root, this node's parent should be updated first.
    if self._parent:
    self._parent.update_recursive(-leaf_value)
    self.update(leaf_value)

  def get_value(self, c_puct):
    """Calculate and return the value for this node.
    It is a combination of leaf evaluations Q, and this node's prior
    adjusted for its visit count, u.
    c_puct: a number in (0, inf) controlling the relative impact of
    value Q, and prior probability P, on this node's score.
    """
    self._u = (c_puct * self._P *
       np.sqrt(self._parent._n_visits) / (1 + self._n_visits))
    return self._Q + self._u

  def is_leaf(self):
    """Check if leaf node (i.e. no nodes below this have been expanded).
    """
    return self._children == {}

  def is_root(self):
    return self._parent is None

class MCTS(object):
  """A simple implementation of Monte Carlo Tree Search."""

  def __init__(self, policy_value_fn, c_puct=5, n_playout=10000):
    """
    policy_value_fn: a function that takes in a board state and outputs
    a list of (action, probability) tuples and also a score in [-1, 1]
    (i.e. the expected value of the end game score from the current
    player's perspective) for the current player.
    c_puct: a number in (0, inf) that controls how quickly exploration
    converges to the maximum-value policy. A higher value means
    relying on the prior more.
    """
    self._root = TreeNode(None, 1.0)
    self._policy = policy_value_fn
    self._c_puct = c_puct
    self._n_playout = n_playout

  def _playout(self, state):
    """Run a single playout from the root to the leaf, getting a value at
    the leaf and propagating it back through its parents.
    State is modified in-place, so a copy must be provided.
    """
    node = self._root
    while(1):
    if node.is_leaf():

      break
    # Greedily select next move.
    action, node = node.select(self._c_puct)
    state.do_move(action)

    action_probs, _ = self._policy(state)
    # Check for end of game
    end, winner = state.game_end()
    if not end:
    node.expand(action_probs)
    # Evaluate the leaf node by random rollout
    leaf_value = self._evaluate_rollout(state)
    # Update value and visit count of nodes in this traversal.
    node.update_recursive(-leaf_value)

  def _evaluate_rollout(self, state, limit=1000):
    """Use the rollout policy to play until the end of the game,
    returning +1 if the current player wins, -1 if the opponent wins,
    and 0 if it is a tie.
    """
    player = state.get_current_player()
    for i in range(limit):
    end, winner = state.game_end()
    if end:
      break
    action_probs = rollout_policy_fn(state)
    max_action = max(action_probs, key=itemgetter(1))[0]
    state.do_move(max_action)
    else:
    # If no break from the loop, issue a warning.
    print("WARNING: rollout reached move limit")
    if winner == -1:  # tie
    return 0
    else:
    return 1 if winner == player else -1

  def get_move(self, state):
    """Runs all playouts sequentially and returns the most visited action.
    state: the current game state

    Return: the selected action
    """
    for n in range(self._n_playout):
    state_copy = copy.deepcopy(state)
    self._playout(state_copy)
    return max(self._root._children.items(),
       key=lambda act_node: act_node[1]._n_visits)[0]

  def update_with_move(self, last_move):
    """Step forward in the tree, keeping everything we already know
    about the subtree.
    """
    if last_move in self._root._children:
    self._root = self._root._children[last_move]
    self._root._parent = None
    else:
    self._root = TreeNode(None, 1.0)

  def __str__(self):
    return "MCTS"
